### 2013-11-09 Article/book/BookSources/chapter3SimpleRules.tex
Book 1st version

% vim:encoding=utf8 ft=tex sts=2 sw=2 et:
% Copyright (c) 2009 Jaroslaw Koszuk
%
% $Id$

\documentclass{tewiart}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{array}
\usepackage{subcaption}

\newtheorem{definition}{Definition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{example}[definition]{Example}

\title{Meaning of simple rules in investment strategies of algorithmic trading}
\headtitle{Meaning of simple rules in investment strategies of algorithmic trading\dots}
\author{Antoni Wiliński\inst{1}, Piotr Błaszyński\inst{1}, Aneta Bera\inst{1}, \\ Wojciech Nowicki\inst{1}, Katarzyna Buda\inst{1}}
\headauthor{Antoni Wiliński, Piotr Błaszyński et al.}
\affiliation{%
  \inst{1}West Pomeranian University of Technology\\
  Faculty of Computer Science\\
  ul. Żołnierska 49, 71-210 Szczecin Poland\\
  \{awilinski, pblaszynski, abera, wnowicki, kbuda\}@wi.zut.edu.pl
}
\keywords{algorithmic trading, forecasting, financial markets, simple rules, computational intelligence, investment strategies}

\begin{document}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{logotewi.png}
\end{figure}

\maketitle

\begin{abstract}
In article are shown studies of the possibly simplest investment strategy of algo trading. The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the proper response, not to forecast, there are almost always opportunities to achieve profit. This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities (eight results included). Introduced the original concept of quadrant of openings on each bar. In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop.
\end{abstract}

@@

@@

@@

\section{The test results}
\indent The charts below show the curves of capital accumulation for each quarter of quadrant. Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average. Fifth diagram shows the (S1s) cumulative strategy value, which is the sum of profit of all open positions at this moment. Obviously all component strategies are calculated for the best parameter for each one of them.\\
\indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength). Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit. Third column, "bestCalmar", represents Calmar Ratio which describes profit-to-maximum drawdown ratio. Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span. Last column "la" presents the number of open positions.
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
\item indices: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

\include{results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\indent Suggested simple strategy is suitable only for algorithmic trading, even in absolute simplest form it seems to be interesting. As it’s been written in the introduction, more from cognitive point of view, than for the transaction value.\\
\indent Surprisingly strategy S1s is a fast and very simple way of receiving really good results, because it is sort of adding each quadrant in one file. In this case results show how surplus grows bigger than loss. \\
\indent This strategy can be modified in many ways.  Eg. in case of suggestions of simultaneous opening long and short positions better is to abandon work than opening both positions (due to transaction costs). The opening of another position in the same direction, eg. long position after closing the previous long position is senseless, it’s better to continue already opened position. These are two simplest ways to improve strategy. There are probably many ways to filter openings that allow to preserve only the most valuable due to profit events. Purpose of this paper was to prove the thesis, that even the simplest strategy has some potential profit, whose using is fascinating challenge.\\
\indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged. \\
\indent Moreover the results prove that depending on the current market characteristics, it is possible to temporarily disable some quarters from trade in order to getting better profits. Certainly parameters still should be calculated in the background, to be included in trade if market characteristic changes.

@@

\end{document}

>>>>

\chapter{Znaczenie prostych zasad w strategiach inwestycyjnych handlu algorytmicznego}
\label{SimpleRules} % Always give a unique label
% use \chaptermark{}
% to alter or adjust the chapter heading in the running head
\section{abstract}
\label{sec:c3abstract}
% Always give a unique label % and use \ref{<label>} for cross-references % and \cite{<label>} for bibliographic references % use \sectionmark{} to alter or adjust the section heading in the running head
In article are shown studies of the possibly simplest investment strategy of algo trading. The authors' intention was to prove the thesis that in the greedy algorithmic trading directed to the proper response, not to forecast, there are almost always opportunities to achieve profit. This paper presents the results of tests for over twenty core markets - currency pairs, indices and commodities (eight results included). Introduced the original concept of quadrant of openings on each bar. In principle, the strategy is not relevant investment (studies were conducted without transaction costs), only cognitive in order to develop.

@@

\label{sec:c3Introduction}

@@

\label{sec:c3StrategyCharacteristics}

@@

\section{The test results}
\label{sec:c3TheTestResults}
\indent The charts below show the curves of capital accumulation for each quarter of quadrant. Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average. Fifth diagram shows the (S1s) cumulative strategy value, which is the sum of profit of all open positions at this moment. Obviously all component strategies are calculated for the best parameter for each one of them.\\
\indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength). Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit. Third column, "bestCalmar", represents Calmar Ratio which describes profit-to-maximum drawdown ratio. Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span. Last column "la" presents the number of open positions.
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
\item indices: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

@@

\input{resultsChapter3Fig1EURJPY}
\input{resultsChapter3Fig2CHFJPY}
\input{resultsChapter3Fig3GBPCHF}
\input{resultsChapter3Fig4FUS500}
\input{resultsChapter3Fig5SILVER}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:c3Conclusions}
\indent Suggested simple strategy is suitable only for algorithmic trading, even in absolute simplest form it seems to be interesting. As it’s been written in the introduction, more from cognitive point of view, than for the transaction value.\\
\indent Surprisingly strategy S1s is a fast and very simple way of receiving really good results, because it is sort of adding each quadrant in one file. In this case results show how surplus grows bigger than loss. \\
\indent This strategy can be modified in many ways.  Eg. in case of suggestions of simultaneous opening long and short positions better is to abandon work than opening both positions (due to transaction costs). The opening of another position in the same direction, eg. long position after closing the previous long position is senseless, it’s better to continue already opened position. These are two simplest ways to improve strategy. There are probably many ways to filter openings that allow to preserve only the most valuable due to profit events. Purpose of this paper was to prove the thesis, that even the simplest strategy has some potential profit, whose using is fascinating challenge.\\
\indent The authors believe, due to observing results of experiments, that the thesis of this dormant potential has been acknowledged. \\
\indent Moreover the results prove that depending on the current market characteristics, it is possible to temporarily disable some quarters from trade in order to getting better profits. Certainly parameters still should be calculated in the background, to be included in trade if market characteristic changes.

@@
